\plaintitle

### 2018-04-04 paper/paper.tex
...

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  When a user wants to ``make the room darker'',
  he should translate it to a real action like ``turn off the ceiling light''.
  To do so,
  he may have to ``toggle the wall switch''
  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his intention
  ``使房黒暗'' into ``make the room darker'',
  translate it to ``turn off the ceiling light'', 
  and finally generate a command string like ``\tt{\$ iot ceilinglight 0}''.

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in a wide area of situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.

\end{abstract}

@@

When people want to perform a task using modern artifacts,
people frequently find difficulty handling them properly.
%
Even when manuals and help systems are provided,
they are usually hard to use because of the
vocabulary problem \cite{Furnas:1987:VPH:32206.32212}.
%
People don't use online help systems\cite{Novick:2006:WDP:1166324.1166329}.
Twitterでのアンケート: 80\% が全然使わない
% https://gyazo.com/2dd525388cce34c916638f51bad386c7

やりたいと思ったことがすぐできればどれほど嬉しいことか
そもそも検索や翻訳が必要なものであるならそれを楽にすればよい

When we use artifacts,
we should translate our vague intentions in our brain into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
All the living creatures seem to be performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.

Even when people almost know what they have to do for what they want to do,
it is often not easy to perform the task properly.
Even when people know that they can watch a movie on the Internet,
finding a movie and playing it is a difficult task for people without experiences.
% even when detailed user manuals and documents exist.
It would be nicer if they could watch a movie on the net
just by showing a vague title or attributes of the movie
in various languages.

@@

We propose a command translation system with which users can generate a complete
command string.
%
We provide a database consisting of
pairs of
(1) the description of the task that users want to perform,
and
(2) the actual command string required by the system.
(1) can be written using regular expressions in any language,

@@

We implemented the {\GH} system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

A powerful information retrieval mechanism called {\EH} is used in {\GH}.

@@

\begin{quote}
  description: \\
  \tt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
  command: \\
  \tt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
\end{quote}

@@

The data used in {\GH} are represented as {\SB} documents.
%
{\SB} is a general-purpose flexible Wiki system for
any kind of data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors, and simple
markup symbols can be used just like MarkDown\footnote{markdown}
and other markup languages.

>>>>

% 部屋を暗くする
% make the room darker 
% iot ......

@@

\begin{abstract}
  We introduce a flexible command translation system that can generate
  a complex command string from vague keywords
  given by the user.
  %
  % Although intuitive GUI are 
  % command-line interface (CLI) is stil widely used everywhere,
  %
  When people use computers to perform tasks,
  there is usually a huge mismatch between the users' intention
  and the required action.
  % the language and vocabularies used for the task are completely different.
  When a user wants to ``make the room darker'',
  he should translate it to a real action like ``turn off the ceiling light''.
  To do so,
  he may have to ``toggle the wall switch''
  or issue a command like ``\tt{\$ iot ceilinglight 0}''.
  If the user is a Chinese speaker, he might have to translate his intention
  % ``使房黒暗'' into ``make the room darker'',
  ``房間暗一点'' into ``make the room darker'',
  ``turn off the ceiling light'', 
  ``toggle the wall switch'',
  and finally to a command like ``\tt{\$ iot ceilinglight 0}''.

  People are perpetually suffering from such multi-level ``\textit{translation gaps}''.
  Translation gaps exist even for experienced computer users, but
  they are serious for vast amount of people around the world.
  %
  We propose a simple and general translation framework
  {\EH} that can be used in various situations
  where such translation is required.
  We show how our framework can be used
  in the {\GH} system
  with which user can easily generate complex \tt{git} commands
  from fragments of users' intentions.
\end{abstract}

@@

When people want to perform a task using modern artifacts,
people frequently find difficulty handling them properly.
%
Even when manuals and help systems are provided,
people don't use them\cite{Novick:2006:WDP:1166324.1166329}
partly because of the vocabulary problem\cite{Furnas:1987:VPH:32206.32212}.
%
% Twitterでのアンケート: 80\% が全然使わない
% https://gyazo.com/2dd525388cce34c916638f51bad386c7
% 
% やりたいと思ったことがすぐできればどれほど嬉しいことか
% そもそも検索や翻訳が必要なものであるならそれを楽にすればよい
%
We should translate our vague intentions in our brain into actions required for the artifacts.
When we want to watch a movie, we may pick up a DVD disk, put it into a
DVD player, push the play button, and set up the audio and the monitor.
When we feel thirsty, we may go to the kitchen, pick up a glass, and
turn the faucet on to fill the glass with water.
All the living creatures are performing such translations
between intentions and actions without difficulty, but
in the modern world, people are suffering from
serious gaps between what they want to do and what they have to do.

Even when people vaguely know what they have to do for what they want to do,
it is often not easy for them to perform the task properly.
Even when people know that they can watch a movie on the Internet,
finding a movie and playing it is a difficult task for people without experiences.
It would be nicer if they could watch a movie on the net
just by showing a vague title or attributes of the movie
in various languages.

@@

We propose a simple, flexible and powerful
command translation framework with which users can generate a complete
command string.
%
We provide a database consisting of
pairs of
(1) the description of the task that users want to perform,
and
(2) the actual command string required by the system.
(1) can be written using regular expressions in any language,

@@

We implemented the ``{\GH}'' system
with which a user can translate his vague intention in various languages
into a complete \tt{git} command
using the {\EH} framework.

@@

A powerful information retrieval mechanism ``{\EH}'' is used in {\GH}.

@@

\begin{quote}
  description: \\
  \stt{Find a (Chinese|Korean|Vietnamese) restaurant \\  in (San Francisco|Chicago|New York) \\  on Yelp.com} \\
  command: \\
  \stt{open 'http://www.yelp.com/search?\\  find\_loc=\$2\&find\_desc=\$1'}
\end{quote}

@@

The data used in {\GH} are represented as ``{\SB}'' documents.
%
{\SB} is a general-purpose real-time Wiki system for data sharing.
{\SB} users can edit the contents of Wiki pages directly
on Web browsers just like text editors,
using simple markup symbols similar to MarkDown\footnote{markdown}
and other markup languages.
